\section{Introduction}
	\paragraph{}{
	This chapter will outline the functional and non-functional requirements of the project, how they will be supported in the system and the techniques used to capture these requirements.
	}		

\section{Techniques for Requirements Capture}	
	\paragraph{}{
	Traditional techniques \cite{ReqEng}, such as surveys, interviews and analysis of existing documentation and systems, were used to capture the requirements of the system.
	%[SQIRO] - Need to get Object Oriented Systems Analysis and Design using UML
	}
	\paragraph{}{
	The process began with background reading into the domain, as outlined in chapter 2. This involved analysing what functions were available under the OBDII standards, as well as the functions supported by the ELM327 device. Overall, this helped to create a base line for the functional requirements of the project.
	%[Reading - what modes are available, what other tools are there etc.]
	}	
	\paragraph{}{
	Once a list of available functions was compiled, a number of similar applications were analysed. This involved finding which functions were implemented, as well as how they were implemented. The functions that each of these applications supported can be found in table \ref{tab:Features} in chapter 2. By analysing how a function was implemented, it served to highlight which non-functional requirements these similar applications supported and which ones the system should support.
	%[Reviewed similar applications]
	}
	\paragraph{}{
	As the system involved communication with vehicles, it was important to interview people within the motor industry. These people included family members, who have extensive experience in the motor industry, and colleagues that I met during my co-operative education. These interviews were qualitative in nature and the participants were asked what they valued most in a diagnostic scan tool. This served to determine what the system needed from a technical aspect, such as which functions to include in order to effectively diagnose a vehicle. An excerpt of the interview transcript can be seen below:\\
	
	\noindent \textbf{Interviewer: }  Have you used diagnostic scan tools before? \\
	\textbf{Interviewee: }  Yes, I have used them frequently \\
	\noindent \textbf{Interviewer: }  What are the most important diagnostic features of diagnostic scan tools to you? \\
	\textbf{Interviewee: }  DTCs and live data. When I diagnose a car, I will look at DTCs first, then I'll look at live data to check if the DTCs are pointing to a valid issue.\\
	%[Spoke to people in industry - Co-op and family]	
	}
	\paragraph{}{
	Although it was important to interview the domain experts, it was equally important to interview the potential end users. During this stage, proxies for the end user were established. These were vehicle owners with no experience in the motor industry and who had encountered issues with their vehicle in the past. An excerpt of the interview transcript can be seen below:\\

	
	\noindent \textbf{Interviewer: }  What are some of your concerns about using this application? \\
	\textbf{Interviewee 1: }  I would be scared of accidentally damaging my car. I don't have any knowledge about how my car works, so I would be worried about making a mistake and what would happen because of it.\\
	\textbf{Interviewee 2: }  I've never used anything like this before, so I wouldn't know where to start.
	%[Spoke to proxies for the end user / stakeholders]
	}

	\paragraph{}{
	By capturing the expectations of individuals with no technical knowledge, it helped to determine how the functions and results should be presented to the user. As the interviewees voiced their concerns, it became clear that the usability and security of the application were the key non-functional requirements.
	}
	
	\paragraph{}{
	Through the use of reading, observation and interviews, the functional and non-functional requirements of the system were successfully captured.
	%[Conclusion, found a balance between technical needs and user needs]
	}
	
\section{Functional Requirements}	
	\paragraph{}{
	A key outcome of capturing the requirements for this project was determining which OBDII modes to support. Due to the time frame of this project, it was impossible to include all modes, so a subset of modes that would be best suited for the target audience had to be selected.
	}
	\paragraph{}{
	After reviewing similar applications and interviewing domain experts, it was decided that the application would include diagnostic data and DTCs. This corresponds to modes 01, 03, 07 and 0A in the OBDII standard. These modes provide a suitable amount of information to allow a user to obtain an understanding of the status of their vehicle, but they also allow the developer to abstract technical information without sacrificing precision.
	}
	\paragraph{}{
	Modes 03, 07 and 0A, representing current, pending and permanent DTCs respectively, provide the means to quickly assess the severity of the issues with the vehicle. The application must display the severity of each DTC type to the end user. If the user needs more information before making a decision, the application must provide additional information on each DTC with minimal use of technical terms.
	}
	\paragraph{}{
	Mode 01, representing current diagnostic data, is more technical than DTCs. However, with the correct level of abstraction and assistance, it can provide the end user with critical information on the issues with their vehicle. The application must display the data in graphical format, so that it can be tracked over a period of time and potentially erroneous or abnormal values must be highlighted for the end user, to assist in their diagnosis.
	}
	\paragraph{}{
	Given the correct guidance, which will be provided by the application, the end user must be able to make an informed decision about the severity of the issues and the cost to repair them, without any technical knowledge.
	}

\section{Non-Functional Requirements}
	\subsection*{\textit{Portability}}
		\paragraph{}{
		To be able to target a large user base, it is important to release the application on multiple systems. For this reason, the system must be portable, so it can be redeployed as an Android or iOS application. To achieve this, the system should leverage the Xamarin framework, and should separate the core functionality of the application from the UI and system dependent features of the application.
		}
	\subsection*{\textit{Extensibility}}
		\paragraph{}{
		Due to the time frame of the project, it is impossible to include all features intended. Also, as new technology becomes available, the application may need to be extended to support it. The system design should consider a modular design where new features, such as supporting a new mode, can be integrated without requiring a restructure of the architecture.
		}
	\subsection*{\textit{Security}}
		\paragraph{}{
		Security can be defined as "a measure of the system's ability to resist unauthorized usage while still providing its services to legitimate users"\cite{SAinP}. As this application is communicating directly with a vehicle, there may be a danger of damage being done to the vehicle and its components. It must be ensured that no harm can be caused by accidental misuse of the application. This will include proper handling of communication, in the event that a user unplugs the ELM327 device during a procedure, as well as providing the user with information on how to use the application correctly.
		}		
	\subsection*{\textit{Usability}}
		\paragraph{}{
		Usability is concerned with how easy it is for the user to accomplish a desired task and the user support the system provides\cite{SAinP}. The application must be intuitive and easy to use for someone with limited technical knowledge of vehicles. This will include limiting the use of technical terms and creating a coherent UI. The application will follow Microsoft's user experience guidelines, so that users of other Windows 10 application will find it easy to use.
		}
