\section{Summary}
	\paragraph{}{
	The objectives of this project were outlined in chapter 1. To determine if the project was a success, it must be evaluated to ensure the objectives were completed. 
		\begin{itemize}
			\item \textbf{Allow users to retrieve diagnostic information from their vehicle}\\
			The system that was developed included the ability to connect to a vehicle, establish communication and retrieve diagnostic information. This information was displayed in a format that a non-technical end user could comprehend.
			
			\item \textbf{Develop a highly extensible and portable system}\\
			The system was highly extensible as it was easy to add new modules during development and required little to no refactoring to implement new features. The system was portable, as it was demonstrated to run on both Android and Windows 10 using the same core code. 

			\item \textbf{Ensure the system cannot cause damage to a vehicle}\\
			The system was developed in a secure manner, so that the end user had no direct line of communication with the vehicle. The application ensured that accidental misuse could not lead to vehicle damage. 
		\end{itemize}
	}
	\paragraph{}{
	The key objectives of the project were achieved, as shown above. The project was also entered in a competition for "Most Commercially Viable FYP". The project came third place overall, further highlighting the success of this project.
	%Objectives were achieved, Won an award
	}
\section{Future Work}
	\paragraph{}{
	There are a number of possibilities for future expansions of the project in the form of adding new functionality and porting the system to new platforms.
	}
			
	\paragraph{}{
	As the project implemented a subset of the modes shown in Table \ref{tab:Modes}, there is scope for extension of the application in this area. This will involve holding exploratory interviews with domain experts, such as mechanics, to determine what new features would complement the existing	functionality of the application.
	%[ADD NEW MODES]
	}
	
	\paragraph{}{
	As a key aspect of the project was the development of a portable system, there is scope for this application to be ported to a number of new platforms. As Xamarin supports porting to iOS, Mac and older Windows platforms, a decision will be made as to which platform will be used. However, it is likely that iOS will be the next platform for the system, as it would make sense to target all mobile platforms first.
	%[PORT TO iOS]
	}